---
title: "Get In Touch"
subtitle: "An events company making a difference"  
author: 
  - "Bertrand"
  - "Sean"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

<<<<<<< HEAD

```{r, include=FALSE}
library(countdown) 
```
```{r broadcast, echo=FALSE}
xaringanExtra::use_broadcast()
```

```{r, include=FALSE}
at <-"Andrea Tuitt"  
```
```{r, include=FALSE}
amr <-"Andy Roberts"
```

```{r, include=FALSE}
bb <-"Bertrand Bhikarry"
```


```{r, include=FALSE}
sm <-"Sean McCoon"
```
```{r, include=FALSE}
et <-"Environment Tobago"
```
```{r, include=FALSE}
ngo <-"Non-profit organisation"
```
```{r, include=FALSE}
ngos <-"Non-profit organisations"
```

```{r, include=FALSE}
thata <-"Tobago Hotel and Tourism Association"
```


```{r xaringan-logo, echo=FALSE}
xaringanExtra::use_logo(
  image_url = "https://drive.google.com/uc?export=view&id=1bGdksPPXUGUGtrIKokOJExEw1lxG3GYn"
)
```


```{r, echo=FALSE}
xaringanExtra::use_webcam(width = 300, height = 225)
```
```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r xaringanExtra, echo=FALSE}
xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))
```


## Intro to Get In Touch
 Welcome. Whos Who in Sport, Recreation, Wellness and Food
=======
## Typography

Text can be **bold**, _italic_, ~~strikethrough~~, or `inline code`.

[Link to another slide](#colors).

### Lorem Ipsum

Dolor imperdiet nostra sapien scelerisque praesent curae metus facilisis dignissim tortor. 
Lacinia neque mollis nascetur neque urna velit bibendum. 
Himenaeos suspendisse leo varius mus risus sagittis aliquet venenatis duis nec.

- Dolor cubilia nostra nunc sodales

- Consectetur aliquet mauris blandit

- Ipsum dis nec porttitor urna sed
>>>>>>> d0bccf8e43a923cbcab7b12451885fb016fa385d

???
In no particular order
---
## Why Get in Touch?

Tobago *and then Trinidad* needs a tourism tier that is

1. profit oriented but aware (of)  

1. negative externalities

1. openings



.footnote[Apologies. We already had the name]

---
## What is?


#### Get In Touch Company Limited

**An event management group focused on recreational, sport and holistic health tourism**

.footnote[The directors are?]

---
## How will GIT work?

.pull-left[ #### Before formation

- mandate (*achieved at 1st meeting*)   

- Legal advice  

- Action after advice  

]


.pull-right[ #### After formation

- Decide on Strategy ( *we are here now*)  
- Internal operation
- Go Get in Touch

]
.footnote[Apologies. Get in Touch was already registered]

???
Incorporators are BB, AMR, RA for ET

---
## Title here 

**Today is `r Sys.Date()`**

T&T is open for business.



Flights are open world over, restrictions are lax but

AWARENESS factors high


*Can we cash in on awareness*?

---

## Sample idea

Plant trees for weddings, deaths other commentorative events (for a fee). Add social media and other forms of long term reporting

On Greehill?


